ms_2_results

### 2017-08-28 man/ms_2_results.Rmd
update writing

>>>>

## Vegetation Greenness
Standardized a

Cuando exploramos las anomalías (brutas, estandarizadas y normalizadas) observamos valores muy negativos para el año 2005. Sin embargo vemos valores menos negativos para 2005. 🔴 Tukey posthoc testing (lsmeans package CITAR) was conducted for pairwise comparisons among the slopes and the disturbance years 🔴

Las anomalías (sa) fueron significativamente menores en 2005 (-2.285 ± 0.029)que para 2012 (-0.418 ± 0.029), (LSMEANS, t.ratio = -45.358; p_value < 0.0001)

Vegetation greenness of *Quercus pyrenaica* forests were lower during the 2005 and 2012 year than the greenness observed for the reference period (Fig 1a :red_circle: EVI profile comparison), particu
